Glyph-maps for visualizing climate data and models

### 2011-08-26 paper.tex
Tweak rescaling graphics

\section{Effect of scale}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{month-rescale-max}%
  \includegraphics[width=0.5\linewidth]{month-rescale01}
  \caption{caption}
  \label{fig:label}
\end{figure}

Other types of scaling: scale range to 0-1 (subtract min and divide by range), standardize mean and standard deviation (or robust variants).

>>>>

\section{Partitioning patterns into shape and size}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.33\linewidth]{month-rescale-none}%
  \includegraphics[width=0.33\linewidth]{month-rescale-max}%
  \includegraphics[width=0.33\linewidth]{month-rescale01}
  \caption{Smoothed de-seasonalized daily temperature glyph-map. (Left) unscaled, (center) scaled to have maximum 1, (right) scaled to have maximum 1 and minimum 0.}
  \label{fig:label}
\end{figure}

Of course other types of scaling are possible. Another classical scaling method is to standardize mean and standard deviation to 0 and 1 (or robust variants).
